The influence of resource use on yield versus quality trade-off in Australian vineyards

### 2023-08-17 article.tex
backup of pdfs

Broad regional differences are summarised in Figure \ref{fig:spider}. The most notable difference is between vineyards within 'Very Hot' and 'Very Dry' (inland) areas where little emphasis is put on achieving high average sale prices, with the focus being on the larger scale yield. Water Use changes dramatically between these regions as well, with water being a driving force in the mass production of grapes but not necessarily the quality. The warmer and drier regions tend to also cater to larger vineyards, with greater areas.

\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{starplots.pdf}}
  \caption{Radar plot of climatic profile's resource use, yield and average sale price.}\label{fig:spider}
\end{figure}

\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{yield_verse_value.pdf}}
  \caption{Scatter plot of vineyard yield against the product of yield and average price per tonne. The axes are in standard deviations with points coloured by climate.}\label{fig:yield_vs_value}
\end{figure}

\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{yield_verse_value.pdf}}
  \caption{Scatter plot of vineyard yield against the product of yield and average price per tonne. The axes are in standard deviations with points coloured by climate.}\label{fig:yield_vs_value}
\end{figure}
%
\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{yield_verse_value_by_area.pdf}}
    \caption{Scatter plot of vineyard yield against the product of yield and average price per tonne as ratios to area harvested. The axes are in standard deviations with points coloured by climate.}\label{fig:yield_vs_value_area}
\end{figure}
%

%
% KM: Are these observed or modelled values?
%
% Replace with star charts?
%
%Observing Figure \ref{fig:yield_vs_value} shows an almost discrete difference between vineyards in 'Hot' areas than other regions. Comparing Figure \ref{fig:yield_vs_value} to Figure \ref{fig:yield_vs_value_area} shows almost opposing trends. However, with area coming into play in Figure \ref{fig:yield_vs_value_area}, many data points are scaled differently; specifically the vineyards from 'Hot' regions change to be found the bottom right tail end, indicating the production of large quantity of lower value grapes. An inconspicuous difference between the Figures, is that a large amount of the difference can be explained by rotation (being $90^\circ$ clockwise from Figure \ref{fig:yield_vs_value} to \ref{fig:yield_vs_value_area}). This is more visible when comparing both graphs to the map of regional averages for response variables, see Figure \ref{fig:map}.

@@

\begin{table}[]
  \label{tab:kfold}
  \caption{Model validation using k-fold cross validation, for 10 folds repeated 100 times.}
  \resizebox{\textwidth}{!}{
  \begin{tabular}{@{}cccc@{}}
    \toprule
    \textbf{} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Mean\\ Squared Error\end{tabular}} & \textbf{R2} & \textbf{\begin{tabular}[c]{@{}c@{}}Mean Average \\ Error\end{tabular}} \\ \midrule
    \textbf{Model 1} & 3.087E-01 & 9.045E-01 & 2.165E-01 \\
    \textbf{Model 2} & 5.104E-01 & 7.409E-01 & 3.493E-01 \\
    \textbf{Model 3} & 1.652E-01 & 9.723E-01 & 1.008E-01 \\
    \textbf{Model 4} & 2.235E-01 & 9.500E-01 & 1.279E-01 \\ \bottomrule
    \end{tabular}
  }
  \end{table}

\section{Discussion}
%Interestingly all but Model 2 do not appear to capture the introduction of Tariffs to Australian exports, which had a pronounced effect within the sale and production of wine in Australia . This needs a wine aus ref and to be put in the discussion

>>>>

Broad regional differences are summarised in Figure \ref{fig:spider}. The most notable difference is between vineyards within 'Hot' and 'Very Dry' (inland) areas where little emphasis is put on achieving high average sale prices, with the focus being on the larger scale yield. Water Use changes dramatically between these regions as well, with water being a driving force in the mass production of grapes but not necessarily the quality. The warmer and drier regions tend to also cater to larger vineyards, with greater areas. 
\par
\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{starplots.pdf}}
  \caption{Radar plot of climatic profile's resource use, yield and average sale price.}\label{fig:spider}
\end{figure}

Figure \ref{fig:yield_vs_value_area} further shows the emphasis that 'Hot' areas have on high yields with low average sale price compared with other regions. Scaling average price and yield by area shows a strong negative trend, trading quantity for higher sales prices.
\par
\begin{figure}
  \resizebox{\textwidth}{!}{
  \includegraphics{yield_verse_value_by_area.pdf}}
    \caption{Scatter plot of vineyard yield against the product of yield and average price per tonne as ratios to area harvested. The axes are in standard deviations with points coloured by climate.}\label{fig:yield_vs_value_area}
\end{figure}

Table \ref{tab:kfold} shows the validation results of each of the models. The $R^2$ measures of fit show similar results to the original models, with a slight decrease. Indicating that the models are robust and consistent.
\par
\begin{table}[]
  \label{tab:kfold}
  \caption{Model validation using k-fold cross validation, for 10 folds repeated 100 times.}
  \resizebox{\textwidth}{!}{
  \begin{tabular}{@{}cccc@{}}
    \toprule
    \textbf{} & \textbf{\begin{tabular}[c]{@{}c@{}}Residual Mean\\ Squared Error\end{tabular}} & \textbf{R2} & \textbf{\begin{tabular}[c]{@{}c@{}}Mean Average \\ Error\end{tabular}} \\ \midrule
    \textbf{Model 1} & 3.087E-01 & 9.045E-01 & 2.165E-01 \\
    \textbf{Model 2} & 5.104E-01 & 7.409E-01 & 3.493E-01 \\
    \textbf{Model 3} & 1.652E-01 & 9.723E-01 & 1.008E-01 \\
    \textbf{Model 4} & 2.235E-01 & 9.500E-01 & 1.279E-01 \\ \bottomrule
    \end{tabular}
  }
  \end{table}

\section{Discussion}
%Interestingly all but Model 2 do not appear to capture the introduction of Tariffs to Australian exports, which had a pronounced effect within the sale and production of wine in Australia . This needs a wine aus ref and to be put in the discussion

%
% KM: Are these observed or modelled values?
%
% Replace with star charts?
%
%

@@
